Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-11-03 supp/index.Rmd
<edit index>

American Southeast, Caddo, NAGPRA, archaeoinformatics, museum studies, digital humanities, non-Western art history, geometric morphometrics, STEM, STEAM, ovoid biface, Jowell knife, Jowell knives, lithics, oblique parallel flaking

@@

The pattern that emerges is one of differential retouch _intensity_, where the isometric reduction strategies of one group (Millsap Cache) articulates with a different reduction practice thought to be associated with locally abundant raw material (Kay County flint). This stands in contrast to the comparatively minimal retouch intensity of another group (Jowell Farm) where local raw material was of poor quality and insufficient size, yielding a situation where it was necessary to import raw material from an extralocal source (Edwards chert).

>>>>

American Southeast, Caddo, NAGPRA, archaeoinformatics, museum studies, digital humanities, non-Western art history, geometric morphometrics, STEM, STEAM, ovoid biface, Jowell knife, Jowell knives, Jowell biface, lithics, oblique parallel flaking

@@

The pattern that emerges is one of differential isometric retouch _intensity_, where the retouch strategies of Caddo knappers from Millsap Cache articulate with a different reduction practice thought to be associated with locally abundant raw material (Kay County flint). This stands in contrast to the comparatively minimal isometric retouch intensity of another group (Jowell Farm) where local raw material was of poor quality and insufficient size, yielding a situation where it was necessary to import raw material from an extralocal source (Edwards chert).
